Evaluation of probabilistic photometric redshift estimation approaches for \boldblue{ \textsc{The Rubin Observatory Legacy Survey of Space and Time} (LSST)}

### 2020-08-21 paper/main.tex
add sentence on Buzzard data request

\section*{Data Availability}
The data underlying this article were provided by the makers of the Buzzard Flock simulation group by permission.  Data will be shared on request with the corresponding authors upon permission of the Buzzard Flock simulation group.  All analysis and plotting scripts used in the writing of this paper are available on GitHub in the \texttt{metric\_scripts} and \texttt{plotting\_scripts} directories of the following repository: \url{https://github.com/LSSTDESC/PZDC1paper}.

>>>>

\section*{Data Availability}
The data underlying this article were provided by the makers of the Buzzard Flock simulation group by permission.  Data will be shared on request to the corresponding authors upon permission of the Buzzard Flock simulation group.  For updated and larger datasets, requests can be made directly to the authors of the Buzzard Flock simulations \citep{DeRose:19}.  All analysis and plotting scripts used in the writing of this paper are available on GitHub in the \texttt{metric\_scripts} and \texttt{plotting\_scripts} directories of the following repository: \url{https://github.com/LSSTDESC/PZDC1paper}.
